How Well do we Teach Cybersecurity?\\(Abstract 20 January, Paper 27th)

### 2018-12-25 ITiCSE2019.tex
More SQL

\subsection{Educational Resources}
It is 15 years since \cite{Guimaraesetal2004} 
wrote ``All the topics listed above should be presented in the first
Database Course'', and the first such topic was SQL injection \cite{Anonymous2018b}. SQL injection has been around fro twenty years \cite{HornerHyslip2017a}. Nevertheless SQL injection is still a major weakness: number one in the OWASP Top 10 \cite{OWASP2017a}.

JHD to write about Database books. \cite{Drop2019}.

>>>>

\subsection{Educational Resources}
It is 15 years since \cite{Guimaraesetal2004} 
wrote ``All the topics listed above should be presented in the first
Database Course'', and the first such topic was SQL injection \cite{SPIDynamics2002,Anonymous2018b}. SQL injection as an attack has been around for twenty years \cite{HornerHyslip2017a}, has its own cartoon (\url{https://xkcd.com/327/}, dating back to 2007 according to the Internet Archive) and website (\url{http://bobby-tables.com/}). Nevertheless SQL injection is still a major weakness: number one in the OWASP Top 10 \cite{OWASP2017a}, and has been in the Top 10 since at least 2003.

Clearly such a major weakness should be well-taught. One would like to think it is, but the first author has yet to meet a UK undergraduate who recalls being taught it \emph{outside} a specialist cyber-security course.  It's hard to determine what is taught, but a reasonable proxy for this is the content of recomended textbooks.

JHD to write about Database books. \cite{Drop2019}. using \cite{StangerMartin2015a}
